Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-20 ba_resubmit/response_to_reviewers.tex

\newpage

\section{Additional Points Addressed}

We highlight some additional points addressed in our revision. \todo
\textcolor{blue}{Brian: These are just some suggestions that I have, so we can chat through these in case you don't agree! I have these marked up on a printed copy of the paper itself to help you more easily make the changes. Please note I have not made these changes, but I'm marking them on a marked up paper so you can go back through and make changes. It's likely that there may be more errors, so please go over things very carefully for all errors as the content is all there, we just have to weed out these tedious details.}

\begin{enumerate}
\item We have added introductory sentences to each section/subsection to provide more guidance to the reader. 
\item The word databases is used throughout instead of files or lists. 
\item We have checked for the proper use of commas throughout the paper. 
\item We have re-written our proposed work on page 2 to make it more clear our contributions to the literature as it was missing our improvements over existing work in terms of speed with minimal loss in accuracy as well as providing two case studies. One case study is from the original paper of our extension, while another case study illustrates our ability to scale to larger databases. We provide a more comprehensive discussion regarding our work. 
\item We have broken up sentences that are too long.
\item We have removed repetitive words, such as intuitive, additionally.  \textcolor{blue}{Brian: you can use something like antidote to check for these or go through yourself. Be careful with the word intuitive. While it might be obvious to you, it may not be obvious to the Editor and this word can be quite jarring). As an example, in my job talk, Mike West did not find the linkage structure to be intuitive and found it to be quite weird and confusing!}
\item We have checked that we define terms before they are introduced. 
\item We have defined the parameters $m$ and $u$ on page 4. 
\item One page 5, section 2.2, we have made it more clear why our extension is warranted and needed in the literature. 
\item We have removed confusing language, such as "compactful representation of" on page 5. 
\item We have checked that fast beta linkage is represented by fabl throughout. 
\item \textcolor{blue}{See page 10 for a long list of comments.}
\item We do not start sentences with a Greek letter or a parameter.
\item We have fixed the sentence ``sampling a value from...." that has a missing verb (see page 11).
\item We have fixed a typo in equation 6, which is a missing (). 
\item We have corrected many typos in section 5.1 page 12 (first paragraph). These include a comma that should not be present, a period instead of a comma, and a Greek letter that starts a sentence.
\item Break up the first long sentence in Lemma 1 as it's hard to read. 
\item "In the simulation results displayed..." This sentence is awkward and should be rephrased. Page 13. 
\item Appendices should be done as A, B, C or the convention in BA (please check). 
\item There is a comma present that needs to be removed in Figure 2. 
\item Page 15, provide a reference to the Appendix.
\item proportion should be proportional on page 15
\item datasets should be databases on page 17
\item bold m and u on page 18
\item Therefore needs a comma after it on page 18
\item equation 7 is not consistent with other equations on page 20
\item Convergence is stated on page 20. We have shown no issue of lack of convergence. Please address. 
\item Conclusion needs to be longer most likely or they will ask us to address this. 
\end{enumerate}
\end{document}

### 2022-09-20 ba_resubmit/response_to_reviewers.tex

\newpage

\section{Additional Points Addressed}

We highlight some additional points addressed in our revision. \todo
\textcolor{blue}{Brian: These are just some suggestions that I have, so we can chat through these in case you don't agree! I have these marked up on a printed copy of the paper itself to help you more easily make the changes. Please note I have not made these changes, but I'm marking them on a marked up paper so you can go back through and make changes. It's likely that there may be more errors, so please go over things very carefully for all errors as the content is all there, we just have to weed out these tedious details.}

\begin{enumerate}
\item We have added introductory sentences to each section/subsection to provide more guidance to the reader. 
\item The word databases is used throughout instead of files or lists. 
\item We have checked for the proper use of commas throughout the paper. 
\item We have re-written our proposed work on page 2 to make it more clear our contributions to the literature as it was missing our improvements over existing work in terms of speed with minimal loss in accuracy as well as providing two case studies. One case study is from the original paper of our extension, while another case study illustrates our ability to scale to larger databases. We provide a more comprehensive discussion regarding our work. 
\item We have broken up sentences that are too long.
\item We have removed repetitive words, such as intuitive, additionally.  \textcolor{blue}{Brian: you can use something like antidote to check for these or go through yourself. Be careful with the word intuitive. While it might be obvious to you, it may not be obvious to the Editor and this word can be quite jarring). As an example, in my job talk, Mike West did not find the linkage structure to be intuitive and found it to be quite weird and confusing!}
\item We have checked that we define terms before they are introduced. 
\item We have defined the parameters $m$ and $u$ on page 4. 
\item One page 5, section 2.2, we have made it more clear why our extension is warranted and needed in the literature. 
\item We have removed confusing language, such as "compactful representation of" on page 5. 
\item We have checked that fast beta linkage is represented by fabl throughout. 
\item \textcolor{blue}{See page 10 for a long list of comments.}
\item We do not start sentences with a Greek letter or a parameter.
\item We have fixed the sentence ``sampling a value from...." that has a missing verb (see page 11).
\item We have fixed a typo in equation 6, which is a missing (). 
\item We have corrected many typos in section 5.1 page 12 (first paragraph). These include a comma that should not be present, a period instead of a comma, and a Greek letter that starts a sentence.
\item Break up the first long sentence in Lemma 1 as it's hard to read. 
\item "In the simulation results displayed..." This sentence is awkward and should be rephrased. Page 13. 
\item Appendices should be done as A, B, C or the convention in BA (please check). 
\item There is a comma present that needs to be removed in Figure 2. 
\item Page 15, provide a reference to the Appendix.
\item proportion should be proportional on page 15
\item datasets should be databases on page 17
\item bold m and u on page 18
\item Therefore needs a comma after it on page 18
\item equation 7 is not consistent with other equations on page 20
\item Convergence is stated on page 20. We have shown no issue of lack of convergence. Please address. 
\item Conclusion needs to be longer most likely or they will ask us to address this. 
\item Reference summary of notation in main paper and make sure it is complete. 
\item Refer the reader back to the main body of appendix with a reference so it's easier to find the section. 
\item Provide an introduction to each subsection so it's more clear what you're presenting. Example: Section 7.2: In this section, we derive the full conditional distributions of section \ref{}. 
\item Similar minor details in appendix that are marked up regarding punctuation/typos.
\end{enumerate}
\end{document}

### 2022-09-20 ba_resubmit/response_to_reviewers.tex

	\pointRaised{R1}{%
	This manuscript addresses the bipartite matching problem in data linkage and proposes a new fast computation version of “Beta Linkage” to allow such matching to take place for pairs of large databases without resorting to ad hoc blocking. It is built upon the Felegi-Sunter model of record linkages, where linkages are made within strata of agreement between records across the two databases, and relies heavily on advances made by Sadinle (2017). Overall, the paper presents a practical implementation of a modified Beta Linkage approach to	matching. It demonstrates that even though the new method suffers from the limitations of not seamlessly enforcing one-to-one matching, it is feasible for large datasets with modest numbers of features on which to match. Though the novelty of the presented methodology is primarily in the computational approach, I believe it to be a real advance for practical implementation of record linkage in modern applications.

	I have no major concerns about the content or accuracy of the presentation. However, substantial improvements are warranted to confirm my impression. In addition to the recommendation made by Reviewer 1 to include more clarity of the novel contributions of this manuscript, I believe that the explanation of the method should be written more clearly, the simulation comparisons should be repeated/expanded, and various features of the simplification should be fleshed out a bit more. Finally, more practical advice would be welcome. All of these points are more specifically described in the itemized list below
	}

	\reply{%
	\textbf{We thank the reviewer (AE) for noticing our computational novelties that expand upon the prior limitations of the prior work of Sadinle (2017). Our revised paper clarifies our novel contributions, improves upon the exposition of the writing, provides practical guidance for users, and expands the simulations. We expand on these points further below.} \todo
	}

	\pointRaised{R1}{%
		Overall, the notation is, somewhat by necessity, quite extensive. However, I’m not convinced that it’s entirely consistent. A glossary in the appendix may help the reader navigate the paper more easily.}
\reply{%
	We have provided a summary of notation in Appendix 7.1. \textcolor{red}{I'm not sure where I should reference this in the text. Do I need to?}
	\textcolor{blue}{I would recommend a table for notation of the model and a table for notation of your hashing method. Why? It will be strange to reference it all together. I would try and put these in the main body if possible as it will really help the reader. You could also write a graphical model with notation of your model to help the reader. These are just some thoughts to think about. (I'm going to leave this up to you Brian if you want to abandon the able as it's quite annoying).}
}

@@

%\textcolor{blue}{This is a good point. I wonder if we could perhaps remove a lot of the notation by Sadinle/FS and redo the notation such that the ordering wouldn't matter. Also, it would make more sense to follow with the examples that we use in the paper -- NLTCS and EL Salvador so that we don't confuse the reader. Let's talk through this point as this would be a big change. If the algorithm and notation can be easily modified to reverse things, this would be a nice addition to the paper and improvement over Sadinle.}

\pointRaised{R1}{%
5. Section 3, full model: $I_obs(.)$ seems to be taken from a different paper dealing with missing fields, which is not at all discussed in this manuscript. This consideration of missing fields and the accompanying discussion of missing data mechanism should be included if such data is to be considered for this manuscript. This comment also applies to the $Gamma^{obs}$ notation in the following subsection.
}

\reply{%
	\textbf{Our missingness assumptions and the definition of $I_{obs}()$ have been added near end of Section 3.} \textcolor{red}{Think about where best to put this.} \textcolor{blue}{I put this somewhere; feel free to move it if you don't like it!}
}

@@

	\section*{Reviewer 3}
	\setcounter{responsectr}{0}

	The paper presents a computational variant of the method introduced by Sadinle (2017). Simulation results are presented and the variant is applied on a new, significantly larger data set. A significant part of the paper is a reproduction of the paper of Sadinle. The variant is introduced in section 4. It is simple but consequential. The simulations and applications show how the variant accelerates the computation relative to the original method and reveals the trade-offs.

	The value of the paper resides in that computational complexity continues to be a difficult obstacle in the application of Bayesian statistics. The proposals of the paper enable the application of Sadinle’s approach to an extent not possible before. It is important to present the research for what it is: An extension of the method of Sadinle motivated by computational considerations. Here Sadinle supersedes Fellegi-Sunter in the sense while the starting point of Sadinle’s research is Fellegi-sunter, the starting point of this paper is Sadinle’s work. This should be made clearer, beginning in the abstract and reiterated in the conclusion.

	\reply{%
	Thank you for your positive feedback regarding our paper. We have clarified that we are motivation by the work of Sadinle and computational considerations. We have tried to make this more clear in both the abstract, introduction, and conclusion.}
		\textcolor{red}{BEKA/JERRY: I think this reviewer wants us to explicitly mention Sadinle in the abstract. I think I had that originally, but we removed it. 
	}

### 2022-09-20 ba_resubmit/kundinger_resubmit.tex
answered q of brian.

\begin{abstract}
Recently, researchers have developed Bayesian versions of the Fellegi Sunter model for record linkage. These have the crucial advantage of quantifying uncertainty from imperfect linkages.  However, current implementations of Bayesian Fellegi Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks.  We propose a variation on Bayesian Fellegi Sunter models that we call fast beta linkage, or \texttt{fabl}.  Specifically, we propose independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large datasets through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} has markedly increased speed with minimal loss of accuracy.

\textcolor{red}{BEKA/JERRY: Reviewer 2 wanted a specific reference to Sadinle in the abstract. I remember we actively decided not to do that. What do you think?}
\end{abstract}

>>>>

\begin{abstract}
Recently, researchers have developed Bayesian versions of the Fellegi Sunter model for record linkage. These have the crucial advantage of quantifying uncertainty from imperfect linkages.  However, current implementations of Bayesian Fellegi Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks.  \textcolor{blue}{We propose a variation on Bayesian Fellegi Sunter models that we call fast beta linkage, or \texttt{fabl}, and is motivated by computational considerations. 
Our method extends that of \cite{sadinle_bayesian_2017}, who extended the early work of \cite{fellegi_theory_1969}.}
Specifically, we propose independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large datasets through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} has markedly increased speed with minimal loss of accuracy.

\textcolor{red}{BEKA/JERRY: Reviewer 2 wanted a specific reference to Sadinle in the abstract. I remember we actively decided not to do that. What do you think?} \textcolor{blue}{I added this back in. He only has one concern, so let's make sure to satisfy the person.}
\end{abstract}
